Spending too much time at the Galactic bar: chaotic fanning of the Ophiuchus stream

### 2016-01-25 ms.tex
back to single column
oops, figure caption

% \keywords{}

@@

% ---------------------------------------------------------------------------------
\begin{figure*}[!tbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{figures/potentials-four}
\caption{{\it Left column:} Circular velocity curves along the Sun-Galactic center line for a representative barred MW potential model (top left) and for the static MW potential model (bottom left). Solid black line shows total (sum of all components), lines below show a decomposition by potential components. Vertical grey bar shows approximate position of the Sun, horizontal grey bar shows roughly the range in measured circular velocity of the Sun. {\it Right column:} Contours of constant surface density for a barred MW potential (top right) and the static MW potential model (bottom right). Four contours are drawn per decade in surface density between $10^7$ and $10^{12}~\msun~{\rm kpc}^{-3}$. Note the perturbation from the bar potential within Galactocentric radius $r \lesssim 4~{\rm kpc}$. The Sun's position is indicated by the `$\odot$' symbol. }
\label{fig:potentials}
\end{center}
\end{figure*}

@@

% ---------------------------------------------------------------------------------
\begin{figure}[!tbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/orbitfits}
\caption{ Results from fitting orbits to BHB stars associated with the Ophiuchus stream in the static and barred potential models. Data used for computing the likelihood are shown as black points with grey error bars. The four ``fanned'' BHB stars from S16 excluded from the likelihood computation are shown as grey squares. Error bars may sometimes be smaller than the point size. Lines (blue) show sections of orbits integrated forward and backwards from initial conditions drawn from the posterior samples generated by MCMC (See Section~\ref{sec:orbitfit}). Note that the four higher dispersion stars (the four stars with highest longitude) were not used when computing the likelihood and are only shown for completeness. Though these four stars are significant outliers relative to the extrapolated orbit, they are (1) at the correct distance and sky position relative to the stream and (2) have velocities $\approx$2.5$\sigma$ discrepant with the halo velocity distribution in this region.}
\label{fig:orbitfits}
\end{center}
\end{figure}

@@

% ---------------------------------------------------------------------------------
\begin{figure}[!tbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/orbit-yz}
\caption{  Projections of orbits integrated from the mean orbital parameters estimated from the orbit fitting posterior distributions in each potential model. Orbits are integrated for 6 Gyr and shown in Galactocentric, Cartesian coordinates. Even though the mean orbital parameters have nearly identical values (e.g., the initial conditions are nearly identical in heliocentric coordinates), the orbits in each potential model are  different in appearance. }
\label{fig:orbits-yz}
\end{center}
\end{figure}

@@

% ---------------------------------------------------------------------------------
\begin{figure}[!tbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/lyapunov-hist}
\caption{ Histograms of estimated Lyapunov time, $\lyapt=1/\lyapexp$, for posterior samples from the orbit fitting procedure (Section~\ref{sec:orbitfit}). More chaotic orbits, i.e. those with shorter Lyapunov times, typically occur in barred potentials with higher pattern speeds. There is little dependence on bar angle. All orbits in these barred potential models are strongly chaotic with $t_\lambda \ll t_{\rm Hubble}$ and $t_\lambda \sim t_{\rm orbit}$, where the typical orbital period for Ophiuchus stream stars is a few hundred Megayears.}
\label{fig:lyapunov-hist}
\end{center}
\end{figure}

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/mockstream-xyz}
\caption{ Star particles (grey points) from mock streams generated on the mean orbits in each potential model shown in projections of Galatocentric, Cartesian coordinates. The position of the Sun is shown as the symbol at $(x,z)=(-8,0)~{\rm kpc}$. The corners of the sky position and distance plots of Figures~\ref{fig:mockstream0}--\ref{fig:mockstream1} are shown transformed to these coordinates as dark markers near $(x,z)=(-4,3)~{\rm kpc}$, $(x,z)=(0,4)~{\rm kpc}$. This demonstrates that the stream is nearly aligned our viewing angle. }
\label{fig:mockstreamxyz}
\end{center}
\end{figure*}

>>>>

\keywords{
  Galaxy: halo
  ---
  globular clusters: general
  ---
  stars: kinematics and dynamics
  ---
  Galaxy: structure
  ---
  Galaxy: kinematics and dynamics
}

@@

% ---------------------------------------------------------------------------------
\begin{figure*}[!tbp]
\begin{center}
%\includegraphics[width=0.7\textwidth]{figures/potentials-four}
\includegraphics[width=\textwidth]{figures/potentials-four}
\caption{{\it Left column:} Circular velocity curves along the Sun-Galactic center line for a representative barred MW potential model (top left) and for the static MW potential model (bottom left). Solid black line shows total (sum of all components), lines below show a decomposition by potential components. Vertical grey bar shows approximate position of the Sun, horizontal grey bar shows roughly the range in measured circular velocity of the Sun. {\it Right column:} Contours of constant surface density for a barred MW potential (top right) and the static MW potential model (bottom right). Four contours are drawn per decade in surface density between $10^7$ and $10^{12}~\msun~{\rm kpc}^{-3}$. Note the perturbation from the bar potential within Galactocentric radius $r \lesssim 4~{\rm kpc}$. The Sun's position is indicated by the `$\odot$' symbol. }
\label{fig:potentials}
\end{center}
\end{figure*}

@@

% ---------------------------------------------------------------------------------
\begin{figure}[!tbp]
\begin{center}
%\includegraphics[width=0.5\textwidth]{figures/orbitfits}
\includegraphics[width=0.75\textwidth]{figures/orbitfits}
\caption{ Results from fitting orbits to BHB stars associated with the Ophiuchus stream in the static and barred potential models. Data used for computing the likelihood are shown as black points with grey error bars. The four ``fanned'' BHB stars from S16 excluded from the likelihood computation are shown as grey squares. Error bars may sometimes be smaller than the point size. Lines (blue) show sections of orbits integrated forward and backwards from initial conditions drawn from the posterior samples generated by MCMC (See Section~\ref{sec:orbitfit}). Note that the four higher dispersion stars (the four stars with highest longitude) were not used when computing the likelihood and are only shown for completeness. Though these four stars are significant outliers relative to the extrapolated orbit, they are (1) at the correct distance and sky position relative to the stream and (2) have velocities $\approx$2.5$\sigma$ discrepant with the halo velocity distribution in this region.}
\label{fig:orbitfits}
\end{center}
\end{figure}

@@

% ---------------------------------------------------------------------------------
\begin{figure}[!tbp]
\begin{center}
%\includegraphics[width=0.5\textwidth]{figures/orbit-yz}
\includegraphics[width=\textwidth]{figures/orbit-yz}
\caption{  Projections of orbits integrated from the mean orbital parameters estimated from the orbit fitting posterior distributions in each potential model. Orbits are integrated for 6 Gyr and shown in Galactocentric, Cartesian coordinates. Even though the mean orbital parameters have nearly identical values (e.g., the initial conditions are nearly identical in heliocentric coordinates), the orbits in each potential model are  different in appearance. }
\label{fig:orbits-yz}
\end{center}
\end{figure}

@@

% ---------------------------------------------------------------------------------
\begin{figure}[!tbp]
\begin{center}
%\includegraphics[width=0.5\textwidth]{figures/lyapunov-hist}
\includegraphics[width=\textwidth]{figures/lyapunov-hist}
\caption{ Histograms of estimated Lyapunov time, $\lyapt=1/\lyapexp$, for posterior samples from the orbit fitting procedure (Section~\ref{sec:orbitfit}). More chaotic orbits, i.e. those with shorter Lyapunov times, typically occur in barred potentials with higher pattern speeds. There is little dependence on bar angle. All orbits in these barred potential models are strongly chaotic with $t_\lambda \ll t_{\rm Hubble}$ and $t_\lambda \sim t_{\rm orbit}$, where the typical orbital period for Ophiuchus stream stars is a few hundred Megayears.}
\label{fig:lyapunov-hist}
\end{center}
\end{figure}

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/mockstream-xyz}
\caption{ Star particles (grey points) from mock streams generated on the mean orbits in each potential model shown in projections of Galatocentric, Cartesian coordinates. The position of the Sun is shown as the symbol at $(x,z)=(-8,0)~{\rm kpc}$. The volume of the sky position and distance plots of Figures~\ref{fig:mockstream0}--\ref{fig:mockstream1} are shown transformed to these coordinates as the blue wedge near $(x,z)=(-2,4)~{\rm kpc}$. This demonstrates that the stream is nearly aligned our viewing angle. }
\label{fig:mockstreamxyz}
\end{center}
\end{figure*}
